---
title: Dashboard
author: Jerrin Joe Varghese
date: '2017-10-02'
slug: dashboard
categories:
  - Data visualization
tags:
  - dplyr
  - ggiraph
  - ggplot
  - lahman
---

#Dashboards

#### To use Dashboard, we also have to use one more package called 'flexdashboard': 



* Using Dashboards we can plot different graphs together.

_Lets plot some graphs for using it in the Dashboard._

First graph

#extracting the data I want.
```{r}
result<-Batting%>%
  filter(playerID=='ruthba01')%>%
  select(yearID,SO,HR)
```


* Lets plot first graph based on Strike out and Homeruns

_ visualize the data using scatter plot._
```{r}
ggplot()+
  geom_point(data=result,aes(x=SO,y=HR))+
  xlab("Strike outs")+
  ylab("Homeruns")
```


* Lets plot second graph based on Homeruns
_ visualize the data using Line plot._
```{r}
ggplot()+
  geom_histogram(data=result,aes(x=HR),color='white',bins=15)+
  xlab("Homeruns")
```


  
* Lets plot third graph based on Homeruns and yearID.
_ visualize the data using point and line
plot._
```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR))+
  geom_line(data=result,aes(x=yearID,y=HR))+
  xlab("Year")+
  ylab("Homeruns")

```




* If we need to use side bar, then we have to use below code for doing that

Inputs {.sidebar}
---------------------------------------------------------
Babe Ruth was a power hitter for the New York Yankee's in the 20's and 30's.
He held the record for most homeruns hit in a season until the 60's.

#### To checkout the dashboard, Please go to below link :
https://github.com/jvargh81/BLOG_ON_DS/blob/master/content/post/index.html

